Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-26 paper/main.tex
results: handling & deleting minor todos/comments

\begin{itemize}
    \item adopt some phrasing from the Speech-Anno-Paper
    \item there is no "cue about" in the English language? alternatives are
        "give a hint on/about", "indicate"; changes the sentences but should
        ask Alex
\end{itemize}

@@

\begin{itemize}
    \item kürzen (war nicht ganz einfach)
    \item table of results: how many decimal points?
    \item how much details regarding procedure in Sengupta?
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
    \item check if captions of figs and tables now (really) match phrasing
        in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.\todo{phrasing to delineate from Huth
(2016)}
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

We hypothesize[d] that an exclusively auditory stimulus can/could localize
``visual area'' in individual subjects and thus possibly substitute a
block-design experiment using pictures.
% hypo b
Further, we hypothesize[d] that an exclusively auditory stimulus can/could
localize the PPA in individual subjects, and thus substitute a visual experiment
be which would be more practicable to assess brain functions in visually
impaired persons.
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions the block-designed
visual localizer.\todo{interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lastly, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

@@

\todo[inline]{das Verschieben des Sounds in den Segmenten spiegelt sich auch in
den unterschiedlichen Counts der Events je Segment wider (AV Bild vs AV Sound vs
AO Sound)}

@@

\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe
jetzt lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AD und
AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das
bedeutet); COH: what is better: reference to table as it is now (more precise,
but harder to read) or use non-cryptic words in the figure?}

@@

\todo[inline]{why was done? narrator and cuts to other setting are "somewhat"
correlated; and now what? -> cf. discussion, part "random shower thoughts"}
% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
contrasting nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory hint of switching to another
setting.

@@

\todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
genommen, FFA ist ja kartiert (Julia Caspers); COH: probaly the caption was
invisible in the version Simon got? changed the size of the figure so the
caption is now on the page}

@@

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{check that}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

@@

\todo[inline]{if we here report procedure of Sengupta as detailed as it is now
(imo too long), we probably need to explain the differences between strict,
relaxed, simple in more detail in the method section and not just reference to
Sengupta}

@@

% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $z$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
\citep{sengupta2016extension}).
% procedure a)
Starting with the most conservative contrast (\textit{strict} set) and a
threshold of t = 2.5, we looked for clusters with at least 20 voxels (using
AFNI).
% procedure b)
We titrated [?] the threshold in the range of [2, 3] until we found an isolated
cluster for the PPA.
% Sengupta: procedure b)
If a cluster was not found or not isolated, we used a contrast from the
\textit{relaxed} set, or finally the \textit{simple} set\todo{not used for PPA},
and repeated the process until we found a cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we used the same contrast of each
naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset. \todo{Neurovault does not like unstandardized spaces}
% here report in group space
For better comparisons of subjects, we report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension}.
% MNI space
The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

\todo[inline]{BA-plots only shortly mentioned now}
% Bland-Altman-Plots
To better depict the agreement and difference between individual results of the
visual localizer and the primary AD contrast, we created Bland-Altman-Plot that
visualize mean and difference of two spatially corresponding $z$-values (see
Figure \ref{fig:bland-altman}).
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

\todo[inline]{I tried to keep it concise but detailed; individual contrasts
are given but as numbers}

@@

% AD PPA contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r)
% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
% 4 PPA (l/r); RSC (l/r), LOC (l/r)
% 5 PPA (l/r); RSC (l/r), LOC (-/-)
% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
% 8 PPA (-/-); RSC (-/-), LOC (-/-)

% AD
Reliably across the five contrasts of the AV stimulus, we find bilaterally
significant clusters also in the ventral precuneal cortex and posterior
cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
occipital cortex (contrasts 1, 2, 4, 5)
% AD; LOC: AV cluster are more medial, AD clusters are more lateral
Reliably across the five contrasts of the AD stimulus, we find bilaterally
significant clusters in the ventral precuneus (all except contrasts 8), lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
right in contrast 2).

% non-systematic
Lastly, contrast 2 of the AD stimulus  also shows bilateral clusters in the
anterior cingulate gyrus and right paracingulate gyrus (frontal medial cortex),
right putamen, and right frontal pole.
%
Contrast 3 shows clusters bilaterally in the anterior cingulate gyrus and left
frontal pole.
%
Contrast 6 shows one additional cluster also in the right medial frontal
cortex.\todo{fsleyes (again) to match text such that clusters in Figure 5 are
easily attributable to region}

@@

\todo[inline]{Discussion: explains how results fill gap identified in
intro}

\todo[inline]{typically done by recapitulating the results, discussing
limitations, and then revealing how the central contribution may catalyze future
progress}

\todo[inline]{provides caveats to the interpretation describes how the paper
advances the field by providing new opportunities}

@@

>>>>

\begin{itemize}
    \item adopt some phrasing from the Speech-Anno-Paper
    \item there is no "cue about" in the English language? Alternatives are
        "give a hint on/about", "indicate"; changed the sentences but should
        ask Alex
\end{itemize}

@@

\begin{itemize}
    \item how much details regarding procedure in Sengupta?
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
    \item results allg. kürzen (war nicht ganz einfach)
    \item table of results: how many decimal points?
    \item check if captions of figs and tables now (really) match phrasing
        in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

We hypothesize[d] that an exclusively auditory stimulus can/could localize
``visual area'' in individual subjects and thus possibly substitute a
block-design experiment using pictures.
% hypo b
Further, we hypothesize[d] that an exclusively auditory stimulus can/could
localize the PPA in individual subjects, and thus substitute a visual experiment
be which would be more practicable to assess brain functions in visually
impaired persons.
% results: group
On a group average level,
% operationalization in naturalistic stimuli
results demonstrate that our approach based on annotations [of two ecologically
more valid stimuli] to operationalize spatial perception lead to increased
hemodynamic activity in [roughly] the same brain regions the block-designed
visual localizer.\todo{give an interpretation?}
% anterior vs. posterior
On both a group and individual subject level, a comparison of results from the
three datasets also suggests functional differences between the anterior and
posterior PPA.
% what does it mean
The current data add evidence to the hypothesis that the PPA might consist of
submodules that work together during visual perception of landscapes (cf.
\citep{baldassano2013differential}).
%
Lastly, our results suggest that the PPA's anterior part can be localized in
individual subjects by contrasting high-level semantic information occurring in
an auditory naturalistic stimulus.

@@

\todo[inline]{das Verschieben des Sounds in den Segmenten spiegelt sich auch in
den unterschiedlichen Counts der Events je Segment (s. Tabelle 1 \& 3) wider (AV
Bild vs AV Sound vs AO Sound)}

@@

\todo[inline]{SE: Die Abkürzungen in Figure 1: Da steigt keiner hinter}

@@

% control contrasts
Finally, we created several contrasts as negative control for both stimuli.
% AV: no cut > cut
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
regressor (\texttt{vno\_cut} to cut-related regressors \ref{tab:av-contrasts}).
% AV: narrator
One contrast (\texttt{vs\_new} > \texttt{vpe\_old}) was created by
contrasting nouns spoken by the narrator.
% AD stimulus
For the AD stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts as cuts might possibly be correlated with a
change of the soundscape also giving an auditory hint of switching to another
setting.

\todo[inline]{nouns indicating switch to setting  and cuts to other setting are
"somewhat" correlated; cf. results -> discussion, part "random shower thoughts"}

@@

\todo[inline]{Bland-Altman-Plots: Welche Areale habt ihr als masks
genommen, FFA ist ja kartiert (Julia Caspers)}

@@

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap that we gained from the visual localizer experiment.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas gives 3 different most prob. locations depen.
on voxel}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.
% concluding statement
\todo[inline]{any concluding statement here or merely report the clusters?}

@@

@@

\todo[inline]{if we report procedure of Sengupta as detailed as it is now in the
following paragraph (imo it's too long), we probably need to explain the
differences between strict, relaxed, simple set in more detail in the method
section}
% Sengupta et al., 2016
The visual localizer experiment \citep{sengupta2016extension} yielded bilateral
[parahippocampal] clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (sub-04, sub-20).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $z$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts
(\textit{strict}, \textit{relaxed}, and \textit{simple} stimulus set, cf.
\citep{sengupta2016extension}).
% procedure a)
Starting with the most conservative contrast (\textit{strict} set) and a
threshold of t = 2.5, we looked for clusters with at least 20 voxels (using
AFNI).
% procedure b)
We titrated [?] the threshold in the range of [2, 3] until we found an isolated
cluster for the PPA.
% Sengupta: procedure b)
If a cluster was not found or not isolated, we used a contrast from the
\textit{relaxed} set, or finally the \textit{simple} set\todo{not used for PPA},
and repeated the process until we found a cluster that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we used the same contrast of each
naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset. \todo{Neurovault does not like unstandardized spaces}
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension}.
% MNI space
The $z$-maps and PPA outline are overlayed on the co-registered MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

\todo[inline]{BA-plots only shortly mentioned now}
% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see Figure \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus AD) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axis).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

@@

\todo[inline]{I tried to keep following part concise but detailed; individual
contrasts are given but as numbers}

@@

% AD PPA contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r)
% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
% 4 PPA (l/r); RSC (l/r), LOC (l/r)
% 5 PPA (l/r); RSC (l/r), LOC (-/-)
% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C.; left frontal pole
% 8 PPA (-/-); RSC (-/-), LOC (-/-)

% AD
Reliably across the five contrasts of the AV stimulus, we find bilaterally
significant clusters also in the ventral precuneal cortex and posterior
cingulate gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral
occipital cortex (contrasts 1, 2, 4, 5).
% AD; LOC: AV cluster are more medial, AD clusters are more lateral
Across the five contrasts of the AD stimulus, we find bilaterally
significant clusters in the ventral precuneus (all except contrasts 8), lateral
occipital cortex (bilateral in contrasts 1 to 4; unilateral in contrasts 6 and
7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
right in contrast 2).

% non-systematic
Lastly, some contrasts of the AD stimulus yielded signficant clusters in regions
that were not statistically signficant in three or more contrasts.
%
Contrast 2 yielded clusters in the anterior cingulate gyrus
(bilateral), right frontal pole, right frontal medial cortex, and right
putamen.
%
Contrast 3 shows clusters in the anterior cingulate gyrus (bilateral), left
frontal pole, and left insular.
%
Contrast 7 shows clusters in the left frontal pole and left frontal operculum
[border to triangularis], left insular.
%
Contrast 6 shows one additional cluster in the right medial frontal cortex.

@@

@@

% Discussion: explains how results fill gap identified in intro

% typically done by recapitulating the results, discussing limitations, and then
% revealing how the central contribution may catalyze future
% progress

% provides caveats to the interpretation describes how the paper
% advances the field by providing new opportunities
